### 2020-03-06 README.Rmd
fix #749 fix #803 EOL no longer requires an API key remove key parameter for EOL functions throughout make use_eol fxn defunct use https instead of http for eol api redo readme removing mention of needing an eol api key add vcr caching in tests for eol fxns
fix #799 make http to https upgrades where possible

You need API keys for Encyclopedia of Life (EOL), Tropicos, IUCN, and NatureServe.

@@

	<td style="text-align:left;"><a href="http://www.itis.gov/ws_description.html">link</a></td>

@@

	<td style="text-align:left;"><a href="http://apiv3.iucnredlist.org/api/v3/docs">link</a></td>
	<td style="text-align:left;"><a href="http://apiv3.iucnredlist.org/api/v3/token">link</a></td>

@@

	<td style="text-align:left;"><a href="http://data.canadensys.net/vascan/api">link</a></td>

@@

	<td style="text-align:left;"><a href="http://cybertaxonomy.eu/eubon-utis/doc.html">link</a></td>

@@

	<td style="text-align:left;"><a href="http://www.marinespecies.org/aphia.php?p=webservice">link</a></td>

>>>>

You need API keys for Tropicos, IUCN, and NatureServe.

@@

	<td style="text-align:left;"><a href="https://www.itis.gov/ws_description.html">link</a></td>

@@

	<td style="text-align:left;"><a href="https://apiv3.iucnredlist.org/api/v3/docs">link</a></td>
	<td style="text-align:left;"><a href="https://apiv3.iucnredlist.org/api/v3/token">link</a></td>

@@

	<td style="text-align:left;"><a href="https://data.canadensys.net/vascan/api">link</a></td>

@@

	<td style="text-align:left;"><a href="https://cybertaxonomy.eu/eubon-utis/doc.html">link</a></td>

@@

	<td style="text-align:left;"><a href="https://www.marinespecies.org/aphia.php?p=webservice">link</a></td>
